Aggression Exploration

### 2016-02-11 ms.tex
cts contests

    \item Aggressiveness, determined by two inheritable traits $k$, $E_0$
    Trade offs:
    \begin{itemize}
        \item more likely to engage in fights with a low probability of winning
    \end{itemize}

    \item search radius, the radius of a searching male (can be thought of as line of sight), See Fig. \ref{fig:area searched}.
    Trade offs:
    \begin{itemize}
        \item higher metabolic cost of search
    \end{itemize}

>>>>

    \item aggression 0 ($\beta$) called $e_0$
    \item aggression 1 ($\alpha$)

    \item Search radius, the radius of a searching male (can be thought of as line of sight), See Fig. \ref{fig:area searched}.
    Trade offs:
    \begin{itemize}
        \item higher metabolic cost of search
    \end{itemize}

### 2016-02-11 scrap/aggression.Rmd
cts contests

This is for exploring aggression levels with the two inheritable traits "E_0" and "K"
Currently E_curr is the actual current energy of the male, I think that it would be better if it were a % of max?

@@

k_min <- 0
k_max <- 2
e_0_min <- -2
e_0_max <- 2

L <- 2

get_level_plotable <- function (e_current){
  old_aggression <- function(L, k, e_0){
    L / (1 + exp(-k*(e_current - e_0)))
  }
  k_val <- seq(k_min, k_max, by = 0.01)
  e_0_val <- seq(e_0_min, e_0_max, by = 0.01)
  r <- raster(outer(k_val, e_0_val, function(a, b){ old_aggression(L, a, b)}), 
              xmn = k_min,
              xmx = k_max,
              ymn = e_0_min,
              ymx = e_0_max)
  return(r)
}
my_theme <- BuRdTheme()

@@

levelplot(get_level_plotable(1), margin=FALSE, xlab = "K", ylab = "E_0", main = "Aggression", at = my_at, colorkey = my_ckey, par.settings=my_theme)

@@

half energy (e_current = 0.5)

```{R}
levelplot(get_level_plotable(0.5), margin=FALSE, xlab = "K", ylab = "E_0", main = "Aggression", at = my_at, colorkey = my_ckey, par.settings=my_theme)
```

close to 0 energy (e_current = 0.1)
```{R}

levelplot(get_level_plotable(0.1), margin=FALSE, xlab = "K", ylab = "E_0", main = "Aggression", at = my_at, colorkey = my_ckey, par.settings=my_theme)

>>>>

This is for exploring aggression levels with the two inheritable traits "E_0" and "K"
Currently E_curr is the actual current energy of the male?

@@

k_min <- -5
k_max <- 5
e_0_min <- -5
e_0_max <- 5
L <- 2
k_val <- seq(k_min, k_max, by = 0.01)
e_0_val <- seq(e_0_min, e_0_max, by = 0.01)

get_level_plotable <- function (e_current){
  old_aggression <- function(L, k, e_0){
    L / (1 + exp(-k*(e_current - e_0)))
  }
  return(raster(outer(k_val, e_0_val, function(a, b){ old_aggression(L, a, b)}), 
              xmn = k_min,
              xmx = k_max,
              ymn = e_0_min,
              ymx = e_0_max)
  )
}
my_theme <- BuRdTheme()

@@

levelplot(get_level_plotable(1), margin = FALSE, 
          xlab = "K", 
          ylab = "E_0",
          main = "Aggression, energy = 100%", 
          at = my_at, 
          colorkey = my_ckey,
          par.settings = my_theme)

@@

This kind of scaling is limited by a upper and lower being $0$ and $L$.

Does this makes sense though? Why?? it seems like an arbitrary constraint and another parameter that the model maybe sensitive to.
I also think that  having it be a funciton of current energy might be too strong an assumption.

Do spiders really have a sense of how much energy they have "left"?

Maybe Aggression should instead be the function inside of the logit ie
$$ P(escalation) = logit^{-1}(f(male_i, male_j)$$

the aggression of male $i$ against $j$ is now a function $f$.

Some low order polynomial maybe:
I think maybe of the difference in normalised mass:

$$\bar{M_i} = \frac {M_i} {M_i + M_j}$$

$$\bar{M_j} = \frac {M_j} {M_i + M_j}$$

$$\Delta \bar{M} = \bar{M_i} - \bar{M_j}$$

$$f(male_i, male_j) = g(\Delta M) = \beta + \alpha \cdot \Delta M $$

Where the trait values:
$$\alpha , \beta$$
are inerited and selected for

'
```{R}
poly_1 <- function (k, e_0, delta_m) {
  e_0 + k*delta_m
}
m <- outer(k_val, e_0_val, function (k, e_0) {poly_1 (k, e_0, 0)})
levelplot(raster(m,
                 xmn = k_min,
                 xmx = k_max,
                 ymn = e_0_min,
                 ymx = e_0_max), 
          main = "linear aggression",
          xlab = "K", 
          ylab = "E_0")
```
